% !TEX root = ../main.tex

\chapter{Outroduction}
\label{ch:observations}

\startcontents[chapters]

\vfill

\begin{alltt}\sffamily
Yet my state is well,
is to take those things for bird,
and God keep him out of my sight,
I do spy some marks of love in her.

With catlike watch,
I have watch'd and travell'd hard,
and some will mourn in ashes,
so that hardly can I check my eyes from tears.

Pillars of the state,
word out of his right sense,
first emperor of Rome Mark Anthony.

Have you had quiet guard,
though art a guard too wanton for the head,
of each other's watch.
\end{alltt}

\newpage
\minicontents
\spirals


% \begin{comment}
%   abusing tech in creative ways can yield useful results
%   pataphysics = Creativity

%   combining the pseudo philosophy of pataphysics with semantically structured algorithms which use programming APIs and computational linguistics to produce original creative works.

%   overturn expectations
%   subvert browsing
%   undermine relevance
%   corrupt results
% \end{comment}

The research presented in this thesis was described in terms of pataphysics, creativity, and technology. These themes span across several disciplines such as literature, philosophy, art, cognitive science, \ac{AI}, linguistics, and computer science.

Using \acf{AMC} 

The current state of the art

Computers which are truly artificially intelligent might be capable of true artificial creativity. Until then they are (philosophical) zombie robots: machines that behave like humans but aren't conscious. The only alternative is to see any computer creativity as a direct or indirect expression of human creativity using digital means and evaluate it as such. \ac{AMC} is neither machine creativity nor human creativity---it is both. By acknowledging the undeniable link between computer creativity and its human influence (the machine is just a tool for the human) we enter a new realm of thought. How is \ac{AMC} defined and evaluated? This thesis address this issue. 

\begin{enumerate}
  \item a practical demonstration of \ac{AMC}
  \item a theoretical framework to help interpret and evaluate products of \ac{AMC}
\end{enumerate}


The overall research methodology was described in chapter~\ref{ch:methodology}\sidepar{§~\ref{ch:methodology}} but it can be summarised as follows.

\begin{description}[leftmargin=3cm]
  \item [Epistemology] Transdisciplinary, subjective
  \item [Methodology] Creative computing, exploratory, experimental
  \item [Methods] Artefact, literature synthesis, algorithm design, theoretical framework, critical reflection and analysis, rapid incremental prototyping
\end{description}



The general process of my project was as follows.

\begin{enumerate}
  \item Critically analyse and synthesise existing literature,\sidepar{\textspiral~\ref{p:lit}}
  \item develop pataphysical algorithms,\sidepar{\textspiral~\ref{p:practice}}
  \item design a system to demonstrate algorithms,\sidepar{\textspiral~\ref{p:practice}}
  \item develop a website as an artefact,\sidepar{\textspiral~\ref{p:practice}}
  \item define an evaluation and interpretation framework,\sidepar{\textspiral~\ref{p:theory}}
  \item analyse results.\sidepar{\textspiral~\ref{p:analysis}}
\end{enumerate}

\section{Observations}

 In the end a transdisciplinary approach was chosen as described in chap XYZ with a heavy component of iterative exploratory rapid-prototyping to develop an artefact to demonstrate what \ac{AMC} is. 

This artefact is presented on \url{pata.physics.wtf}. It is an artwork dedicated to \ac{AMC}, pataphysics, \ac{OULIPO} and programming culture.

A critique of computer creativity and its current evaluation formed the starting point for a new framework which was introduced in chap XYZ. The general conlcusion of the thesis was made up of the critical analysis and further work chapters as awell as this final concluding chapter right at the end.

The appendix contains various code snippets and peripheral pieces vaguely related or relevant for parts of this thesis. The code of the website is included on a CD CHECK attached to the back of the front cover. Of course the website is also available online at \url{pata.physics.wtf}.

\todo{check if i need to submit a CD?}


\section{Issues}

\begin{itemize}
  \item Summarise issues in analysis Section
  \item summarize future work
\end{itemize}

\begin{itemize}
  \item Polymorphism (generalisation) opposes particularity.
  \item Precision opposes exceptions and contradictions.
  \item Logic and structure oppose the imaginary and paradox.
  \item Cross-compatibility opposes the mutually exclusive.
  \item Responsiveness opposes the specific.
  \item Relevance opposes the creative.
\end{itemize}





\section{Answers}
\label{s:answers}

In the introduction I asked several questions that I attempted to asnwer with my research. This section contains brief answers from 50.000 feet\footnote{Inspired by Time Berners-Lee's articles on the Web in 1998---/url{http://www.w3.org/DesignIssues/Architecture.html}}, meaning they provide a top-down view of the answer and pointers to where in the thesis readers can find more elaborations.

\begin{itemize}
  \item What is the relationship between pataphysics and creativity?
  \item How might pataphysics be used to enable or enhance creativity?
  \item How is computer creativity related to artificial intelligence?
  \item Is there a clear distinction between computationally automated or emulated creative processes and the programmer's input?
  \item How can a machine's creative output be evaluated?
  \item How can these evaluatuative systems be improved?
  \item How can information retrieval be infused with creativity?
\end{itemize}

\todo{add chapter references}
\todo{these are closed questions, not research questions}
\begin{description}
  \item[Can computers or algorithms be considered creative?] In short: no. In chapters~\ref{ch:evaluation}\sidepar{§~\ref{ch:evaluation}} and~\ref{ch:interpretation}\sidepar{§~\ref{ch:interpretation}} I have gone into great detail of why I believe that this cannot happen any time soon (see argument of zombies). They can be `creative' (adj/adv CHECK) but the source of the creativity is the programmer of the machine not the machine itself.
  \item[Can pataphysics facilitate creativity?] Yes. Pataphysics provides many principles which can be turned into technicques and constraints which is well known to be able to support creativity (see chapter~\ref{ch:foundations}\sidepar{§~\ref{ch:foundations}}). This is also evident in the \ac{OULIPO} and their use of constraints (see chapter~\ref{ch:creativity}\sidepar{§~\ref{ch:creativity}}).
  \item[Can a creative process be automated or emulated by a computer?] Yes, in theory. It mainly depends how you define the creative process and that is fairly subjective. See more in chapter~\ref{ch:creativity}\sidepar{§~\ref{ch:creativity}} and~\ref{ch:interpretation}\sidepar{§~\ref{ch:interpretation}}.
  \item[Can human and computer creativity be objectively measured?] No. As discussed in chapter~\ref{ch:interpretation}\sidepar{§~\ref{ch:interpretation}} since the perception of creativity is subjective it cannot be quantified in objective terms. By providing a framework\sidepar{§~\ref{s:oec}} that takes into account all possible contextually relevant contributors though we can approximate an objective evaluation.
  \item[Can information retrieval be creative?] Yes. There are many ways this can be achieved too as mentioned in chapter~\ref{ch:analysis}\sidepar{§~\ref{ch:analysis}}.
  \item[Can search results be creative rather than relevant?] Yes, although this is also subjective. What is creative to some might not be creative to everybody. The artefact also nicely showed the difference in perception of results simply based on design of the content (see chapter~\ref{ch:analysis}\sidepar{§~\ref{ch:analysis}}).
\end{description}



\section{Contributions}

mention to whom these could be useful

\todo{write more}

This doctoral project can be broken down into four main contributions.

\begin{itemize}
  \item Three pataphysical search algorithms (clinamen, syzygy and antinomy).
  \item A creative exploratory search tool demonstrating the algorithms \url{pata.physics.wtf}.
  \item A set of 7 subjective criteria and 5 objective constraints for defining creativity.
  \item A combined framework for evaluating and interpreting creativity.
\end{itemize}

In a more practical sense this project has spawned several publications, talks and exhibitions (a full list is in preface~\ref{ch:pubs}\sidepar{sec~\ref{ch:pubs}}). Further talks were given by Andrew Hugill at various conferences and events throughout the world where he mentioned my work. My publications were cited in other academic publications and my website was mentioned on Reddit\footnote{Although absolutely nobody seemed interested in it. No idea who posted it or how he found it.}. My job here is done.


\section{And Finally}

\emph{Pataphysics is the science\ldots}

\stopcontents[chapters]
