% !TEX root = ../main.tex

\pagestyle{empty}

\chapter{Publications}
\label{ch:pubs}

\textbf{Fania Raczinski}, Dave Everitt (2016) \emph{``Creative Zombie Apocalypse: A Critique of Computer Creativity Evaluation''}. Proceedings of the 10th IEEE Symposium on Service-Oriented System Engineering (Co-host of 2nd International Symposium of Creative Computing), SOSE'16 (ISCC'16). Oxford, UK. Pages 270--276.

\textbf{Fania Raczinski}, Hongji Yang and Andrew Hugill (2013) \emph{``Creative Search Using Pataphysics''}. Proceedings of the 9th ACM Conference on Creativity and Cognition, CC'13. Sydney, Australia. Pages 274--280.

Andrew Hugill, Hongji Yang, \textbf{Fania Raczinski} and James Sawle (2013) \emph{``The pataphysics of creativity: developing a tool for creative search''}. Routledge: Digital Creativity, Volume 24, Issue 3. Pages 237--251.

James Sawle, \textbf{Fania Raczinski} and Hongji Yang (2011) \emph{``A Framework for Creativity in Search Results''}. The 3rd International Conference on Creative Content Technologies, CONTENT'11. Rome, Italy. Pages 54--57.

\spirals

Funding was provided to attend ISCC 2016 in Oxford by Jon Bennett, Clinton Ingrams and a Graduate School Travel Award.

A travel fund has been awarded by the DMU Faculty of Technology for travel to Australia, Sydney for the Creativity and Cognition conference in July 2013.

De Montfort University has granted me a full 3 year bursary covering living costs and tuition fees.

\spirals

\todo{update}

IOCT Student Showcase 07 June 2016

Conference talk on ``Creative Zombie Apocalypse'' (by Fania Raczinski and Dave Everitt) at ISCC in Oxford, UK, 29 March 2016.

Phoenix CAS talk on ``Pata-computed Poetry'' in Leicester, UK, 14 Oct 2015.

De Montfort University Leicester Media School Launch Showcase, 05 November 2014.

De Montfort University Institute of Creative Technologies PhD showcase at the Phoenix Cube Gallery, Leicester, 15--18 August 2014.

Conference talk on ``'' at Creativity and Cognition in Syndey, Australia, 20 June 2013.

TDC talk on ``The Pataphysics of the Future'' (by Andrew Hugill, Hongji Yang and Fania Raczinski) in Leicester, UK, 13 Feb 2013.

\clearpage
